---
title: "WAPTS_L@S_work_in_progress"
format: html
editor: visual
---

# WAPTS Codebase for L\@S work in progress submission

We will use this code base to provide a base for simulations that we run
in WAPTS work.\

# Part I: Policy codebase

We will outline the following adaptive policy algorithms used in the
paper.

## Policy 1: Uniform Random Policy

```{r}
UR_multi <- function(success_rates, n, burnin = 1, batch = 1) {
  # by default let's make sure the pb is the correct arm
  # List: tracking successes and failures under each arm
  # ex. [0,1,1,1,2,3,3,4,5,6], final index value indicates total number of successes/failures
  K = length(success_rates)
  # add delta:
  p_star <- max(success_rates)
  delta <- p_star - success_rates
  outcomes = list()
  for (k in 1:K){
    outcomes[[paste("arm", k, sep = "_")]] = rbinom(n, 1, success_rates[k])
  }

  arm_successes <- array(0, dim=c(K, n))
  arm_failures <- array(0, dim=c(K, n))
  
  # List: tracking only the current number of successes and failures (Value changes for each iteration)
  arm_s <- rep(0, K)
  arm_f <- rep(0, K)

  # History that tracks if there the correct arm is allocated
  # ex. [1,0,1,1,0,1] 1 indicates the correct arm was allocated for the trial, 0 indicates a wrong arm is allocated, we'll make the assumption that only the last arm is correct
  abl <- c()
  history <- c()
  regret <- c()
  
  AP = c()
  
  arm_selected <- c()
  
  # ---------- BURNIN PERIOD: use Uniform Random (UR) sampling only ----------
  
  for (i in 1:n) {
    
    draw_arms <- runif(K) # randomly drawing one arm out of all arms
    arm_chosen <- which.max(draw_arms) # settle down which arm to pick
    AP <- c(AP, 0.5)
    
    arm_selected[i] <- arm_chosen 
    
    if(arm_chosen == which.max(success_rates)){
      abl[i] <- 1
    }
    else{
      abl[i] <- 0
    }
    history[i] <- outcomes[[paste("arm", arm_chosen, sep = "_")]][i]

    if (history[i] == 1) {
      arm_s[arm_chosen] <- arm_s[arm_chosen] + 1}
    else {
      arm_f[arm_chosen] <- arm_f[arm_chosen] + 1
      }

    # Tracking the build-up of total number of successes, failures, for arm a & b
    arm_successes[ , i] <- arm_s
    arm_failures[ , i] <- arm_f
    regret[i] <- delta[arm_chosen]
  }
  
  # todo: adding in the calculation on Wald_score:
  final_success <- arm_successes[,n]
  final_failure <- arm_failures[,n]
  
  Wald_score <- c()
  
  p_optimal <- 0 
  try(p_optimal <- final_success[1]/(final_failure[1] + final_success[1]))
  for (k in 2:K){
    if (final_success[k] == 0 & final_failure[k] == 0){
      p_arm <- 0
      p_avg <- p_optimal
    }
    else{
      p_arm <- final_success[k]/(final_failure[k] + final_success[k])
      p_avg <- (final_success[k] + final_success[K])/(final_failure[k] + final_success[k]+ final_failure[K] + final_success[K])
    }
    wald <- (p_optimal - p_arm) / sqrt(p_avg*(1-p_avg)*(1/(final_failure[k]+final_success[k]) + 1/(final_failure[K]+final_success[K])))
    Wald_score <- c(Wald_score, wald)
  }
  reject <-  all(Wald_score > qnorm(1-0.05)) 
  if (is.na(reject) == TRUE){
    reject <- FALSE 
  }
  #return(list(WaldScore = WaldScore[n], reward = reward[n], AP = AP[n], APT = APT))
  #return(c(WaldScore[n], expected_reward, actual_reward, AP[n], APT))
  return(list(arm_successes = arm_successes[,n],
              arm_failures = arm_failures[,n],
              reject = reject,
              correct_rate = sum(abl)/n,
              regret = regret,
              history = history,
              arm_selected = arm_selected,
              arm_success_history = arm_successes,
              arm_failure_history = arm_failures))
}
```

```{r}
# mock trial:
# set.seed(1)
UR_multi(success_rates = c(0.4,0.4,0.6), n = 20)
```

## Policy 2: Sub-Sampled (SS) Greedy Method:

Referring from the following paper:

<https://proceedings.neurips.cc/paper_files/paper/2020/file/12d16adf4a9355513f9d574b76087a08-Paper.pdf>

```{r}
SS_greedy <- function(success_rates, n, burnin = 1, batch = 1) {
  # SS-Greedy (Algorithm 4): sample m arms uniformly, then run Greedy on that subset.
  # Keeps the SAME input signature + returns the SAME list fields as UR_multi().
  #
  # Interpretation of args (to preserve your signature):
  # - burnin: number of initial pulls per arm in the subsample (>=1 recommended)
  # - batch: used as subsample size m when > 1; otherwise defaults to ceiling(sqrt(n))

  K <- length(success_rates)

  # Regret baseline
  p_star <- max(success_rates)
  delta  <- p_star - success_rates

  # Pre-generate outcomes for reproducibility/consistency with UR_multi
  outcomes <- vector("list", K)
  names(outcomes) <- paste("arm", 1:K, sep = "_")
  for (k in 1:K) {
    outcomes[[k]] <- rbinom(n, 1, success_rates[k])
  }

  arm_successes <- array(0, dim = c(K, n))
  arm_failures  <- array(0, dim = c(K, n))

  arm_s <- rep(0, K)
  arm_f <- rep(0, K)

  abl <- rep(0, n)
  history <- rep(NA_integer_, n)
  regret  <- rep(NA_real_, n)
  arm_selected <- rep(NA_integer_, n)

  # --- Subsample size m (without changing your function signature) ---
  m <- if (is.numeric(batch) && length(batch) == 1 && batch > 1) {
    min(K, as.integer(batch))
  } else {
    min(K, as.integer(ceiling(sqrt(n))))
  }

  # Sample subset S uniformly at random (without replacement)
  S <- sample.int(K, size = m, replace = FALSE)
  S <- sample(S)  # randomize the order used in the initial pulls

  # --- Initial phase: pull each arm in S 'burnin' times (or until horizon ends) ---
  burnin <- max(1L, as.integer(burnin))
  t <- 1L
  while (t <= n && t <= m * burnin) {
    arm_chosen <- S[((t - 1L) %% m) + 1L]

    arm_selected[t] <- arm_chosen
    abl[t] <- as.integer(arm_chosen == which.max(success_rates))

    y <- outcomes[[arm_chosen]][t]
    history[t] <- y

    if (y == 1L) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1L
    else         arm_f[arm_chosen] <- arm_f[arm_chosen] + 1L

    arm_successes[, t] <- arm_s
    arm_failures[,  t] <- arm_f
    regret[t] <- delta[arm_chosen]

    t <- t + 1L
  }

  # --- Greedy phase on subset S: always pull empirical best arm in S ---
  while (t <= n) {
    pulls_S <- arm_s[S] + arm_f[S]
    means_S <- ifelse(pulls_S > 0, arm_s[S] / pulls_S, -Inf)

    # Tie-break randomly among the best empirical means
    best_idx <- which(means_S == max(means_S))
    arm_chosen <- S[sample(best_idx, 1L)]

    arm_selected[t] <- arm_chosen
    abl[t] <- as.integer(arm_chosen == which.max(success_rates))

    y <- outcomes[[arm_chosen]][t]
    history[t] <- y

    if (y == 1L) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1L
    else         arm_f[arm_chosen] <- arm_f[arm_chosen] + 1L

    arm_successes[, t] <- arm_s
    arm_failures[,  t] <- arm_f
    regret[t] <- delta[arm_chosen]

    t <- t + 1L
  }

  # --- A reasonable "reject" flag (keeps your output field) ---
  # Here: compare empirical best arm in S vs every other arm in S via a Wald z-test on proportions.
  # If any comparison is undefined, we set reject = FALSE.
  pulls_S <- arm_s[S] + arm_f[S]
  means_S <- ifelse(pulls_S > 0, arm_s[S] / pulls_S, NA_real_)
  best_arm <- S[which.max(means_S)]

  z_alpha <- qnorm(1 - 0.05)
  reject <- TRUE
  for (arm_k in setdiff(S, best_arm)) {
    n1 <- arm_s[best_arm] + arm_f[best_arm]
    n2 <- arm_s[arm_k]    + arm_f[arm_k]
    if (n1 == 0 || n2 == 0) { reject <- FALSE; break }

    p1 <- arm_s[best_arm] / n1
    p2 <- arm_s[arm_k]    / n2
    p_pool <- (arm_s[best_arm] + arm_s[arm_k]) / (n1 + n2)

    denom <- sqrt(p_pool * (1 - p_pool) * (1/n1 + 1/n2))
    if (!is.finite(denom) || denom <= 0) { reject <- FALSE; break }

    wald <- (p1 - p2) / denom
    if (!is.finite(wald) || wald <= z_alpha) { reject <- FALSE; break }
  }
  if (is.na(reject)) reject <- FALSE

  return(list(
    arm_successes = arm_successes[, n],
    arm_failures  = arm_failures[, n],
    reject        = reject,
    correct_rate  = sum(abl) / n,
    regret        = regret,
    history       = history,
    arm_selected  = arm_selected,
    arm_success_history = arm_successes,
    arm_failure_history = arm_failures
  ))
}
```

```{r}
# sample trial:
set.seed(1)
SS_greedy(success_rates = c(0.4,0.4,0.6), n = 20)
```

## Policy 3: Beta Bernoulli Thompson Sampling (TS)

```{r}
TS_multi <- function(success_rates, n, burnin = 1, batch = 1) {
  # by default let's make sure the pb is the correct arm
  # List: tracking successes and failures under each arm
  # ex. [0,1,1,1,2,3,3,4,5,6], final index value indicates total number of successes/failures
  K = length(success_rates)
  # add delta:
  p_star <- max(success_rates)
  delta <- p_star - success_rates
  outcomes = list()
  for (k in 1:K){
    outcomes[[paste("arm", k, sep = "_")]] = rbinom(n, 1, success_rates[k])
  }

  arm_successes <- array(0, dim=c(K, n))
  arm_failures <- array(0, dim=c(K, n))
  
  # List: tracking only the current number of successes and failures (Value changes for each iteration)
  arm_s <- rep(0, K)
  arm_f <- rep(0, K)

  # History that tracks if there the correct arm is allocated
  # ex. [1,0,1,1,0,1] 1 indicates the correct arm was allocated for the trial, 0 indicates a wrong arm is allocated, we'll make the assumption that only the last arm is correct
  abl <- c()
  history <- c()
  regret <- c()
  
  AP = c()
  
  arm_selected <- c()
  
  # ---------- BURNIN PERIOD: use Uniform Random (UR) sampling only ----------
  
  for (i in 1:burnin) {
    
    draw_arms <- runif(K) # randomly drawing one arm out of all arms
    arm_chosen <- which.max(draw_arms) # settle down which arm to pick
    
    arm_selected[i] <- arm_chosen 
    
    if(arm_chosen == which.max(success_rates)){
      abl[i] <- 1
    }
    else{
      abl[i] <- 0
    }
    history[i] <- outcomes[[paste("arm", arm_chosen, sep = "_")]][i]

    if (history[i] == 1) {
      arm_s[arm_chosen] <- arm_s[arm_chosen] + 1}
    else {
      arm_f[arm_chosen] <- arm_f[arm_chosen] + 1
      }

    # Tracking the build-up of total number of successes, failures, for arm a & b
    arm_successes[ , i] <- arm_s
    arm_failures[ , i] <- arm_f
    regret[i] <- delta[arm_chosen]
  }
  
  # ---------- AFTER BURNIN PERIOD: Use TS or UR depending on difference between posterior probabilities ----------
  
  for (i in (burnin + 1):n) {

    # Posterior probability updates happen by batch size (whenever m becomes 0, larger batch size -> slower updates)
    m = i %% batch 
    
    # Draw from Beta(alpha, beta) distribution, using only the current success & failure counts 
    # alpha = current successes, beta = current failures of each arm
    # CASE 1: Posterior probability of arms a & b is updated
    if (m == 0) {
      draw_arms <- rbeta(K, arm_successes[, i - 1] + 1, arm_failures[, i - 1] + 1)
      
      # AP_i just for place holder for now, not really calculating it
      AP_i <- 0
      AP <- c(AP, AP_i)
    }
    # CASE 2: Posterior probability of arms a & b is not updated
    else {
      draw_arms <- rbeta(K, arm_successes[, i - m] + 1, arm_failures[, i - m] + 1)
        
    # Using index [i - m] shows we are using the posterior probabilities from the previous batch, and not our most current success/failure counts
    }
    # select the chosen arm to choose
    arm_chosen <- which.max(draw_arms)
    arm_selected[i] <- arm_chosen 
    
    # adding on to the correct allocation rate
    if(arm_chosen == which.max(success_rates)){
      abl[i] <- 1
    }
    else{
      abl[i] <- 0
    }
    
    # record history of the success/failure of that select arm
    history[i] <- outcomes[[paste("arm", arm_chosen, sep = "_")]][i]
    
    
    # Update arm a & b history (abl), successes, and failures
    if (history[i] == 1) {
      arm_s[arm_chosen] <- arm_s[arm_chosen] + 1  # Update success count for chosen arm
    } else {
      arm_f[arm_chosen] <- arm_f[arm_chosen] + 1  # Update failure count for chosen arm
    }
    
    # Tracking the build-up of total number of successes, failures, for arm a & b, adding onto successes and failures from burnin period
    arm_successes[ , i] <- arm_s
    arm_failures[ , i] <- arm_f
    regret[i] <- delta[arm_chosen]
  }

  # List: complete history of number of times arms a & b were chosen (final index, total number of times chosen for each)
  
  # todo: adding in the calculation on Wald_score:
  final_success <- arm_successes[,n]
  final_failure <- arm_failures[,n]
  
  Wald_score <- c()
  
  p_optimal <- 0 
  try(p_optimal <- final_success[1]/(final_failure[1] + final_success[1]))
  for (k in 2:K){
    if (final_success[k] == 0 & final_failure[k] == 0){
      p_arm <- 0
      p_avg <- p_optimal
    }
    else{
      p_arm <- final_success[k]/(final_failure[k] + final_success[k])
      p_avg <- (final_success[k] + final_success[K])/(final_failure[k] + final_success[k]+ final_failure[K] + final_success[K])
    }
    wald <- (p_optimal - p_arm) / sqrt(p_avg*(1-p_avg)*(1/(final_failure[k]+final_success[k]) + 1/(final_failure[K]+final_success[K])))
    Wald_score <- c(Wald_score, wald)
  }
  reject <-  all(Wald_score > qnorm(1-0.05)) 
  if (is.na(reject) == TRUE){
    reject <- FALSE 
  }
  #return(list(WaldScore = WaldScore[n], reward = reward[n], AP = AP[n], APT = APT))
  #return(c(WaldScore[n], expected_reward, actual_reward, AP[n], APT))
  return(list(arm_successes = arm_successes[,n],
              arm_failures = arm_failures[,n],
              reject = reject,
              correct_rate = sum(abl)/n,
              regret = regret,
              history = history,
              arm_selected = arm_selected,
              arm_success_history = arm_successes,
              arm_failure_history = arm_failures))
}
```

```{r}
# mock trial:
set.seed(1)
TS_multi(success_rates = c(0.4,0.4,0.6), n = 20)
```

## Policy 4: Epsilon-Greedy Thompson Sampling (epsilon-TS)

The code does **TS with probability** $\epsilon$ and **Greedy with
probability** $1-\epsilon$.

Referred from the following paper:

<https://arxiv.org/html/2403.00540v1>

```{r}
epsilon_TS_multi <- function(success_rates, n, burnin = 1, batch = 1, epsilon = 0.1) {
  K <- length(success_rates)

  # regret baseline
  p_star <- max(success_rates)
  delta  <- p_star - success_rates

  # pre-generate outcomes (same as your TS_multi)
  outcomes <- list()
  for (k in 1:K) {
    outcomes[[paste("arm", k, sep = "_")]] <- rbinom(n, 1, success_rates[k])
  }

  arm_successes <- array(0, dim = c(K, n))
  arm_failures  <- array(0, dim = c(K, n))

  arm_s <- rep(0, K)
  arm_f <- rep(0, K)

  # pre-allocate
  abl          <- rep(NA_integer_, n)
  history      <- rep(NA_integer_, n)
  regret       <- rep(NA_real_, n)
  AP           <- rep(NA_real_, n)      # placeholder (like yours)
  arm_selected <- rep(NA_integer_, n)

  burnin <- as.integer(max(0, burnin))
  burnin <- min(burnin, n)
  batch  <- as.integer(max(1, batch))
  epsilon <- max(0, min(1, epsilon))

  # helper: random tie-breaking argmax
  argmax_tie_random <- function(x) {
    idx <- which(x == max(x))
    sample(idx, 1)
  }

  # ---------- BURNIN: Uniform Random ----------
  if (burnin > 0) {
    for (i in 1:burnin) {
      arm_chosen <- which.max(runif(K))
      arm_selected[i] <- arm_chosen

      abl[i] <- as.integer(arm_chosen == which.max(success_rates))
      history[i] <- outcomes[[paste("arm", arm_chosen, sep = "_")]][i]

      if (history[i] == 1) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1 else arm_f[arm_chosen] <- arm_f[arm_chosen] + 1

      arm_successes[, i] <- arm_s
      arm_failures[,  i] <- arm_f
      regret[i] <- delta[arm_chosen]
    }
  }

  # ---------- AFTER BURNIN: (1-epsilon) Greedy, epsilon TS ----------
  if (burnin < n) {

    # store last TS posterior sample draw (for batching)
    last_draw <- rep(NA_real_, K)

    for (i in (burnin + 1):n) {

      # Greedy vs TS (per Jin et al. 2023: greedy w.p. 1-epsilon, TS w.p. epsilon)
      do_TS <- (runif(1) < epsilon)

      if (!do_TS) {
        # ---- Greedy: empirical mean using CURRENT counts ----
        pulls <- arm_s + arm_f
        emp_mean <- ifelse(pulls > 0, arm_s / pulls, -Inf)
        arm_chosen <- argmax_tie_random(emp_mean)

      } else {
        # ---- TS: same batch logic as your TS_multi ----
        m <- i %% batch

        if (m == 0) {
          # update TS posterior draws using latest counts at i-1
          last_draw <- rbeta(K, arm_successes[, i - 1] + 1, arm_failures[, i - 1] + 1)
          AP[i] <- 0  # placeholder
        } else {
          # reuse previous batch draw
          if (any(is.na(last_draw))) {
            # first time TS happens before any "m==0" update: draw from latest counts
            last_draw <- rbeta(K, arm_successes[, i - 1] + 1, arm_failures[, i - 1] + 1)
          }
        }

        arm_chosen <- argmax_tie_random(last_draw)
      }

      arm_selected[i] <- arm_chosen
      abl[i] <- as.integer(arm_chosen == which.max(success_rates))

      history[i] <- outcomes[[paste("arm", arm_chosen, sep = "_")]][i]

      if (history[i] == 1) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1 else arm_f[arm_chosen] <- arm_f[arm_chosen] + 1

      arm_successes[, i] <- arm_s
      arm_failures[,  i] <- arm_f
      regret[i] <- delta[arm_chosen]
    }
  }

  # ---------- Wald score block: kept as-is (your original logic) ----------
  final_success <- arm_successes[, n]
  final_failure <- arm_failures[, n]

  Wald_score <- c()
  p_optimal <- 0
  try(p_optimal <- final_success[1] / (final_failure[1] + final_success[1]))

  for (k in 2:K) {
    if (final_success[k] == 0 && final_failure[k] == 0) {
      p_arm <- 0
      p_avg <- p_optimal
    } else {
      p_arm <- final_success[k] / (final_failure[k] + final_success[k])
      p_avg <- (final_success[k] + final_success[K]) /
        (final_failure[k] + final_success[k] + final_failure[K] + final_success[K])
    }
    wald <- (p_optimal - p_arm) / sqrt(p_avg * (1 - p_avg) *
      (1 / (final_failure[k] + final_success[k]) + 1 / (final_failure[K] + final_success[K])))
    Wald_score <- c(Wald_score, wald)
  }

  reject <- all(Wald_score > qnorm(1 - 0.05))
  if (is.na(reject)) reject <- FALSE

  return(list(
    arm_successes = arm_successes[, n],
    arm_failures  = arm_failures[, n],
    reject        = reject,
    correct_rate  = sum(abl, na.rm = TRUE) / n,
    regret        = regret,
    history       = history,
    arm_selected  = arm_selected,
    arm_success_history = arm_successes,
    arm_failure_history = arm_failures
  ))
}
```

```{r}
# mock trial:
set.seed(1)
epsilon_TS_multi(success_rates = c(0.4,0.4,0.6), n = 20)
```

## Policy 5: Beta-Bernoulli Weighted Allocation Probability Adjusted Thompson Sampling (WAPTS) 

This is the main policy that we used for the paper

```{r}
WAPTS_multi_countscale_arm <- function(success_rates, n, burnin = 1, batch = 1,
                                       rescue = FALSE,
                                       w_min = 0.2, w_max = 1.0, c = 20) {

  select_random_max <- function(rate_vector) {
    max_val  <- max(rate_vector, na.rm = TRUE)
    max_inds <- which(rate_vector == max_val)
    if (length(max_inds) == 0) stop("No maximum found.")
    if (length(max_inds) == 1) return(max_inds)
    sample(max_inds, 1)
  }

  K <- length(success_rates)
  p_star <- max(success_rates)
  delta <- p_star - success_rates

  outcomes <- vector("list", K)
  for (k in 1:K) outcomes[[k]] <- rbinom(n, 1, success_rates[k])

  arm_successes <- array(0, dim=c(K, n))
  arm_failures  <- array(0, dim=c(K, n))
  arm_s <- rep(0, K); arm_f <- rep(0, K)

  abl <- rep(NA_integer_, n)
  history <- rep(NA_integer_, n)
  regret  <- rep(NA_real_, n)
  arm_selected <- rep(NA_integer_, n)

  for (i in 1:burnin) {
    arm_chosen <- select_random_max(runif(K))
    arm_selected[i] <- arm_chosen
    abl[i] <- as.integer(arm_chosen == which.max(success_rates))
    history[i] <- outcomes[[arm_chosen]][i]
    if (history[i] == 1) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1 else arm_f[arm_chosen] <- arm_f[arm_chosen] + 1
    arm_successes[, i] <- arm_s
    arm_failures[, i]  <- arm_f
    regret[i] <- delta[arm_chosen]
  }

  for (i in (burnin + 1):n) {

    gamma <- K/(K+sqrt(i))
    m <- i %% batch
    t_idx <- if (m == 0) (i - 1) else (i - m)

    s_prev <- arm_successes[, t_idx]
    f_prev <- arm_failures[, t_idx]
    N_prev <- s_prev + f_prev

    post_mean <- ifelse(N_prev == 0, 1/2, (s_prev + 1)/(N_prev + 2))
    arm_rate  <- (1 + post_mean) * post_mean

    # ---- NEW: arm-specific count scaling ----
    w_k <- w_min + (w_max - w_min) * (N_prev / (N_prev + c))

    draw <- rbeta(K, 1 + w_k * s_prev, 1 + w_k * f_prev)

    draw_arms <- if (rescue) (((1 - gamma) * arm_rate + gamma) * draw) else (arm_rate * draw)

    arm_chosen <- select_random_max(draw_arms)
    arm_selected[i] <- arm_chosen
    abl[i] <- as.integer(arm_chosen == which.max(success_rates))
    history[i] <- outcomes[[arm_chosen]][i]

    if (history[i] == 1) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1 else arm_f[arm_chosen] <- arm_f[arm_chosen] + 1
    arm_successes[, i] <- arm_s
    arm_failures[, i]  <- arm_f
    regret[i] <- delta[arm_chosen]
  }

  list(
    correct_rate = mean(abl, na.rm=TRUE),
    regret = regret,
    history = history,
    arm_selected = arm_selected,
    arm_success_history = arm_successes,
    arm_failure_history = arm_failures
  )
}
```

```{r}
select_random_max <- function(rate_vector) {
  max_val  <- max(rate_vector, na.rm = TRUE)
  max_inds <- which(rate_vector == max_val)

  if (length(max_inds) == 0) stop("No maximum found. The rate_vector might be all NA or empty.")
  if (length(max_inds) == 1) return(max_inds)
  sample(max_inds, 1)
}

# ------------------------------------------------------------
# Tempered-WAPTS: WAPTS allocation shaping + tempered TS draws
# ------------------------------------------------------------
WAPTS_multi_tempered <- function(success_rates, n, burnin = 1, batch = 1,
                                 rescue = FALSE,
                                 eta = 0.5,                 # constant tempering (0<eta<=1 typical)
                                 eta_schedule = c("const", "adaptive"),
                                 eta_min = 0.2, eta_max = 1.0) {

  eta_schedule <- match.arg(eta_schedule)

  K <- length(success_rates)
  p_star <- max(success_rates)
  delta <- p_star - success_rates

  # pre-generate outcomes (same as your original setup)
  outcomes <- vector("list", K)
  for (k in 1:K) outcomes[[k]] <- rbinom(n, 1, success_rates[k])

  arm_successes <- array(0, dim = c(K, n))
  arm_failures  <- array(0, dim = c(K, n))
  arm_s <- rep(0, K)
  arm_f <- rep(0, K)

  abl <- rep(NA_integer_, n)
  history <- rep(NA_integer_, n)
  regret <- rep(NA_real_, n)
  arm_selected <- rep(NA_integer_, n)

  AP <- c()

  # -----------------------
  # Burn-in: Uniform random
  # -----------------------
  for (i in 1:burnin) {
    arm_chosen <- select_random_max(runif(K))
    arm_selected[i] <- arm_chosen

    abl[i] <- as.integer(arm_chosen == which.max(success_rates))
    history[i] <- outcomes[[arm_chosen]][i]

    if (history[i] == 1) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1 else arm_f[arm_chosen] <- arm_f[arm_chosen] + 1
    arm_successes[, i] <- arm_s
    arm_failures[, i]  <- arm_f
    regret[i] <- delta[arm_chosen]
  }

  # -----------------------
  # After burn-in
  # -----------------------
  for (i in (burnin + 1):n) {

    gamma <- K / (K + sqrt(i))
    m <- i %% batch

    # choose which time index to use for "stale posterior" under batching
    t_idx <- if (m == 0) (i - 1) else (i - m)

    s_prev <- arm_successes[, t_idx]
    f_prev <- arm_failures[, t_idx]
    tot_prev <- s_prev + f_prev

    # posterior mean used by WAPTS shaping (keep yours, but make it coherent)
    post_mean <- ifelse(tot_prev == 0, 1/2, (s_prev + 1) / (tot_prev + 2))
    arm_rate  <- (1 + post_mean) * post_mean

    # -----------------------
    # Tempering / power posterior
    # -----------------------
    # Constant eta OR adaptive eta (novel combo with WAPTS)
    if (eta_schedule == "const") {
      eta_t <- eta
    } else {
      # adaptive: conservative early (small eta), increase with time
      # You can swap this schedule later; this is a simple monotone ramp.
      frac <- (i - burnin) / (n - burnin)
      eta_t <- eta_min + (eta_max - eta_min) * frac
    }

    # fractional-count Beta posterior: Beta(1 + eta*s, 1 + eta*f)
    draw <- rbeta(K, 1 + eta_t * s_prev, 1 + eta_t * f_prev)

    # rescue mixing (unchanged idea)
    if (rescue) {
      draw_arms <- ((1 - gamma) * arm_rate + gamma) * draw
    } else {
      draw_arms <- arm_rate * draw
    }

    arm_chosen <- select_random_max(draw_arms)
    arm_selected[i] <- arm_chosen

    abl[i] <- as.integer(arm_chosen == which.max(success_rates))
    history[i] <- outcomes[[arm_chosen]][i]

    if (history[i] == 1) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1 else arm_f[arm_chosen] <- arm_f[arm_chosen] + 1
    arm_successes[, i] <- arm_s
    arm_failures[, i]  <- arm_f
    regret[i] <- delta[arm_chosen]

    if (m == 0) {
      AP <- c(AP, 0)
    }
  }

  # ---- Wald scores (kept as-is from your version; not affecting policy) ----
  final_success <- arm_successes[, n]
  final_failure <- arm_failures[, n]

  Wald_score <- c()
  p_optimal <- 0
  try(p_optimal <- final_success[1] / (final_failure[1] + final_success[1]), silent = TRUE)

  for (k in 2:K) {
    if (final_success[k] == 0 && final_failure[k] == 0) {
      p_arm <- 0
      p_avg <- p_optimal
    } else {
      p_arm <- final_success[k] / (final_failure[k] + final_success[k])
      p_avg <- (final_success[k] + final_success[1]) /
        (final_failure[k] + final_success[k] + final_failure[1] + final_success[1])
    }
    wald <- (p_optimal - p_arm) / sqrt(p_avg * (1 - p_avg) *
      (1 / (final_failure[k] + final_success[k]) + 1 / (final_failure[1] + final_success[1])))
    Wald_score <- c(Wald_score, wald)
  }

  reject <- all(Wald_score > qnorm(1 - 0.05))
  if (is.na(reject)) reject <- FALSE

  list(
    arm_successes = arm_successes[, n],
    arm_failures  = arm_failures[, n],
    reject        = reject,
    correct_rate  = mean(abl, na.rm = TRUE),
    regret        = regret,
    history       = history,
    arm_selected  = arm_selected,
    arm_success_history = arm_successes,
    arm_failure_history = arm_failures
  )
}
```

The old version of the code:

```{r}
# old version:
select_random_max <- function(rate_vector) {
  max_val  <- max(rate_vector, na.rm = TRUE)
  max_inds <- which(rate_vector == max_val)

  if (length(max_inds) == 0) {
    stop("No maximum found. The rate_vector might be all NA or empty.")
  }
  if (length(max_inds) == 1) {
    return(max_inds)   # <- IMPORTANT
  }
  sample(max_inds, 1)
}

# added rescue functionality here

WAPTS_multi <- function(success_rates, n, burnin = 1, batch = 1, rescue = FALSE) {
  # by default let's make sure the pb is the correct arm
  # List: tracking successes and failures under each arm
  # ex. [0,1,1,1,2,3,3,4,5,6], final index value indicates total number of successes/failures
  K = length(success_rates)
  # add delta:
  p_star <- max(success_rates)
  delta <- p_star - success_rates
  outcomes = list()
  for (k in 1:K){
    outcomes[[paste("arm", k, sep = "_")]] = rbinom(n, 1, success_rates[k])
  }

  arm_successes <- array(0, dim=c(K, n))
  arm_failures <- array(0, dim=c(K, n))

  # List: tracking only the current number of successes and failures (Value changes for each iteration)
  arm_s <- rep(0, K)
  arm_f <- rep(0, K)

  # History that tracks if there the correct arm is allocated
  # ex. [1,0,1,1,0,1] 1 indicates the correct arm was allocated for the trial, 0 indicates a wrong arm is allocated, we'll make the assumption that only the last arm is correct
  abl <- c()
  history <- c()
  regret <- c()

  AP = c()

  arm_selected <- c()

  # ---------- BURNIN PERIOD: use Uniform Random (UR) sampling only ----------

  for (i in 1:burnin) {

    draw_arms <- runif(K) # randomly drawing one arm out of all arms
    arm_chosen <- select_random_max(draw_arms) # settle down which arm to pick

    arm_selected[i] <- arm_chosen

    if(arm_chosen == which.max(success_rates)){
      abl[i] <- 1
    }
    else{
      abl[i] <- 0
    }
    history[i] <- outcomes[[paste("arm", arm_chosen, sep = "_")]][i]

    if (history[i] == 1) {
      arm_s[arm_chosen] <- arm_s[arm_chosen] + 1}
    else {
      arm_f[arm_chosen] <- arm_f[arm_chosen] + 1
      }

    # Tracking the build-up of total number of successes, failures, for arm a & b
    arm_successes[ , i] <- arm_s
    arm_failures[ , i] <- arm_f
    regret[i] <- delta[arm_chosen]
  }

  # ---------- AFTER BURNIN PERIOD: Use TS or UR depending on difference between posterior probabilities ----------

  for (i in (burnin + 1):n) {

    gamma = K/(K+sqrt(i))

    # Posterior probability updates happen by batch size (whenever m becomes 0, larger batch size -> slower updates)
    m = i %% batch

    # Draw from Beta(alpha, beta) distribution, using only the current success & failure counts
    # alpha = current successes, beta = current failures of each arm

    # CASE 1: Posterior probability of arms a & b is updated
    if (m == 0) {
      tot_prev <- arm_failures[, i - 1] + arm_successes[, i - 1]

      arm_success_rate <- ifelse(tot_prev == 0, 1,
                                 arm_successes[, i - 1] / tot_prev)

      arm_rate <- (1 + arm_success_rate) * arm_success_rate
      # arm_success_rate <- ifelse(arm_failures[, i - 1] + arm_successes[, i - 1] == 0,
      #                    0.5,
      #                 (arm_successes[, i - 1]) / (arm_failures[, i - 1] + arm_successes[, i - 1]))
      # arm_rate <- (1 + arm_success_rate) * arm_success_rate
      draw <- rbeta(K, arm_successes[, i - 1] + 1, arm_failures[, i - 1] + 1)
      score_wapts <- arm_rate * draw
      score_ts    <- draw
      if (rescue) {
        draw_arms <- (1 - gamma) * score_wapts + gamma * score_ts
      }
      else {
        draw_arms <- score_wapts
      }


      # AP_i just for place holder for now, not really calculating it
      AP_i <- 0
      AP <- c(AP, AP_i)
    }
    # CASE 2: Posterior probability of arms a & b is not updated
    else {
      arm_success_rate <- ifelse(arm_failures[, i - m] + arm_successes[, i - m] == 0,
                         1,
                      (arm_successes[, i - m]) / (arm_failures[, i - m] + arm_successes[, i - m]))
      arm_rate <- (1 + arm_success_rate) * arm_success_rate
      draw <- rbeta(K, arm_successes[, i - m] + 1, arm_failures[, i - m] + 1)
      score_wapts <- arm_rate * draw
      score_ts    <- draw
      if (rescue) {
        draw_arms <- (1 - gamma) * score_wapts + gamma * score_ts
      }
      else {
        draw_arms <- score_wapts
      }

    # Using index [i - m] shows we are using the posterior probabilities from the previous batch, and not our most current success/failure counts
    }
    # select the chosen arm to choose
    arm_chosen <- select_random_max(draw_arms)
    # arm_chosen <- which.max(draw_arms)
    arm_selected[i] <- arm_chosen

    # adding on to the correct allocation rate
    if(arm_chosen == which.max(success_rates)){
      abl[i] <- 1
    }
    else{
      abl[i] <- 0
    }

    # record history of the success/failure of that select arm
    history[i] <- outcomes[[paste("arm", arm_chosen, sep = "_")]][i]


    # Update arm a & b history (abl), successes, and failures
    if (history[i] == 1) {
      arm_s[arm_chosen] <- arm_s[arm_chosen] + 1  # Update success count for chosen arm
    } else {
      arm_f[arm_chosen] <- arm_f[arm_chosen] + 1  # Update failure count for chosen arm
    }

    # Tracking the build-up of total number of successes, failures, for arm a & b, adding onto successes and failures from burnin period
    arm_successes[ , i] <- arm_s
    arm_failures[ , i] <- arm_f
    regret[i] <- delta[arm_chosen]
  }

  # List: complete history of number of times arms a & b were chosen (final index, total number of times chosen for each)

  # todo: adding in the calculation on Wald_score:
  final_success <- arm_successes[,n]
  final_failure <- arm_failures[,n]

  Wald_score <- c()

  p_optimal <- 0
  try(p_optimal <- final_success[1]/(final_failure[1] + final_success[1]))
  for (k in 2:(K)){
    if (final_success[k] == 0 & final_failure[k] == 0){
      p_arm <- 0
      p_avg <- p_optimal
    }
    else{
      p_arm <- final_success[k]/(final_failure[k] + final_success[k])
      p_avg <- (final_success[k] + final_success[1])/(final_failure[k] + final_success[k]+ final_failure[1] + final_success[1])
    }
    wald <- (p_optimal - p_arm) / sqrt(p_avg*(1-p_avg)*(1/(final_failure[k]+final_success[k]) + 1/(final_failure[1]+final_success[1])))
    Wald_score <- c(Wald_score, wald)
  }
  reject <-  all(Wald_score > qnorm(1-0.05))
  if (is.na(reject) == TRUE){
    reject <- FALSE
  }
  #return(list(WaldScore = WaldScore[n], reward = reward[n], AP = AP[n], APT = APT))
  #return(c(WaldScore[n], expected_reward, actual_reward, AP[n], APT))
  return(list(arm_successes = arm_successes[,n],
              arm_failures = arm_failures[,n],
              reject = reject,
              correct_rate = sum(abl)/n,
              regret = regret,
              history = history,
              arm_selected = arm_selected,
              arm_success_history = arm_successes,
              arm_failure_history = arm_failures))
}
```

```{r}
# mock trial:
set.seed(1)
WAPTS_multi_tempered(success_rates = c(0.4, 0.4, 0.6),n = 20, rescue = TRUE)
```

## Policy 6: Information Relaxation Thompson Sampling in a Finite Horizon Setting (IRS-FH)

This policy is used to construct policy comparison with WAPTS, this
policy assumes a further that there is a limit on the horizon (number of
participants) inside the experiment.

The policy is found at this place:

<https://papers.nips.cc/paper_files/paper/2019/file/e5b294b70c9647dcf804d7baa1903918-Paper.pdf>

```{r}
IRS_FH_multi <- function(success_rates, n, burnin = 1, batch = 1) {

  K <- length(success_rates)
  p_star <- max(success_rates)
  delta <- p_star - success_rates

  # pre-generate outcomes per arm (same style as your TS/WAPTS sims)
  outcomes <- vector("list", K)
  for (k in 1:K) outcomes[[k]] <- rbinom(n, 1, success_rates[k])

  arm_successes <- array(0, dim = c(K, n))
  arm_failures  <- array(0, dim = c(K, n))

  arm_s <- rep(0, K)
  arm_f <- rep(0, K)

  history      <- numeric(n)
  regret       <- numeric(n)
  arm_selected <- integer(n)
  abl          <- integer(n)  # correctness indicator

  best_arm <- which.max(success_rates)

  # ---------- burnin: uniform random ----------
  for (i in 1:burnin) {

    arm_chosen <- which.max(runif(K))
    arm_selected[i] <- arm_chosen

    y <- outcomes[[arm_chosen]][i]
    history[i] <- y

    if (y == 1) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1
    else        arm_f[arm_chosen] <- arm_f[arm_chosen] + 1

    arm_successes[, i] <- arm_s
    arm_failures[,  i] <- arm_f

    regret[i] <- delta[arm_chosen]
    abl[i]    <- as.integer(arm_chosen == best_arm)
  }

  # ---------- after burnin: IRS-FH index ----------
  for (i in (burnin + 1):n) {

    m <- i %% batch

    # use stale batch counts like your TS/WAPTS structure
    idx <- if (m == 0) i - 1 else i - m

    # sample a posterior parameter for each arm
    post_pis <- rbeta(K, arm_successes[, idx] + 1, arm_failures[, idx] + 1)

    # finite-horizon “look-ahead” via Binomial shortcut:
    # remaining steps including current i: (n - i + 1)
    future <- n - i + 1
    S_future <- rbinom(K, size = future, prob = post_pis)

    draw_arms <- (arm_successes[, idx] + 1 + S_future) /
                 (arm_successes[, idx] + arm_failures[, idx] + 2 + future)

    arm_chosen <- which.max(draw_arms)
    arm_selected[i] <- arm_chosen

    y <- outcomes[[arm_chosen]][i]
    history[i] <- y

    if (y == 1) arm_s[arm_chosen] <- arm_s[arm_chosen] + 1
    else        arm_f[arm_chosen] <- arm_f[arm_chosen] + 1

    arm_successes[, i] <- arm_s
    arm_failures[,  i] <- arm_f

    regret[i] <- delta[arm_chosen]
    abl[i]    <- as.integer(arm_chosen == best_arm)
  }

  return(list(
    arm_successes = arm_successes[, n],
    arm_failures  = arm_failures[, n],
    correct_rate  = sum(abl) / n,
    regret        = regret,
    history       = history,
    arm_selected  = arm_selected,
    arm_success_history = arm_successes,
    arm_failure_history = arm_failures
  ))
}
```

```{r}
# mock trial:
set.seed(1)
IRS_FH_multi(success_rates = c(0.4, 0.4, 0.6),n = 20)
```

# Part II: Set Up of the Experiment and Simulation Comparison

In this section, let's plan out the simulation and experiment setting of
the study. For each of the setup, we will outline the experiment set up,
and compare the following of reward, regret, lenient regret, posterior
convergence of optimal arm, posterior convergence of most exploit arm.

There are two setups of the experiment in our case:

-   when there is a unique optimal arm in the experiment, i.e. one is
    optimal, and the rest of arms is uniformly below the optimal arm.

-   when there is more than one unique optimal arm in the experiment,
    i.e. at least more than one arm is optimal, the rest of the arms are
    uniformly below the good arms.

## Part II-1 Experiment Setup of Unique Optimal Arm.

### Part II-1.1 Flexible Gap Setting

In this setup, in the simulation setting, we have one arm out of the `K`
arms to be truly optimal, the rest of the arm is uniformly distributed
from the range `(0.5, 0.5 + effect size - 10e-6).` We will plan out the
simulation setting and plot the posterior mean estimate of the optimal
arm, the average reward comparison, and the probability of selecting the
optimal arm.

```{r}
library(dplyr)
library(ggplot2)
library(purrr)

# --- settings ---
burnin    <- 10
n         <- 239
seeds     <- 1024:3024
effect_sizes <- c(0.05, 0.10, 0.20, 0.30)
theta_min <- 0.50

# Generate success rates for flexible gap with a unique best arm
gen_rates_flex <- function(K = 10, theta_min = 0.5, Delta = 0.1, eps = 1e-6) {
  theta_star <- theta_min + Delta
  subs <- pmin(runif(K - 1, min = theta_min, max = theta_star), theta_star - eps)
  c(theta_star, subs)  # optimal arm at index 1
}

run_simulation_flex <- function(seed, method_func, Delta, ..., eps_lenient) {
  set.seed(seed)
  rates <- gen_rates_flex(K = 10, theta_min = theta_min, Delta = Delta)

  out <- method_func(success_rates = rates, burnin = burnin, n = n, ...)

  Succ <- out$arm_success_history
  Fail <- out$arm_failure_history

  # ---- Track A: optimal arm posterior mean (empirical) ----
  s_opt <- Succ[1, ]
  f_opt <- Fail[1, ]
  tot_opt <- s_opt + f_opt
  est_opt <- ifelse(tot_opt > 0, s_opt / tot_opt, NA_real_)
  
  # Bia estimate:
  theta_true <- theta_min + Delta   # = 0.5 + effect size
  bias_opt <- est_opt - theta_true

  # ---- Track B: empirical average reward up to time t ----
  y <- as.numeric(out$history)           # 0/1 reward each step
  avg_reward <- cumsum(y) / seq_len(n)   # cummean

  # ---- Track C: probability of selecting the correct arm up to time t ----
  chosen <- as.integer(out$arm_selected)
  p_correct <- cumsum(chosen == 1L) / seq_len(n)

  # ---- Track D: epsilon-lenient regret up to time t ----
  # r_t^eps = max(0, (theta* - eps) - theta_{a_t})
  theta_star <- max(rates)
  theta_chosen <- rates[chosen]
  inst_regret_eps <- pmax(0, (theta_star - eps_lenient) - theta_chosen)
  regret_eps_cummean <- cumsum(inst_regret_eps) / seq_len(n)

  # ---- Track E: probability of selecting a truly bad arm up to time t ----
  # truly bad: theta_k < theta* - eps
  bad_set <- which(rates < (theta_star - eps_lenient))
  is_bad <- chosen %in% bad_set
  p_bad <- cumsum(is_bad) / seq_len(n)

  data.frame(
    horizon  = rep(seq_len(n), times = 5),
    estimate = c(bias_opt, avg_reward, p_correct, regret_eps_cummean, p_bad),
    target   = rep(c(
      "Optimal arm (1): bias (posterior mean - true)",
      "Average reward up to t",
      "P(select optimal arm) up to t",
      "Avg epsilon-lenient regret up to t (eps=0.5*Delta)",
      "P(select truly bad arm) up to t (eps=0.5*Delta)"
    ), each = n)
  )
}


aggregate_estimates <- function(sim_list, method_name, effect_size) {
  bind_rows(sim_list, .id = "rep") |>
    group_by(target, horizon) |>
    summarise(
      estimate_mean = mean(estimate, na.rm = TRUE),
      ci_lower      = quantile(estimate, 0.025, na.rm = TRUE),
      ci_upper      = quantile(estimate, 0.975, na.rm = TRUE),
      .groups = "drop"
    ) |>
    mutate(method = method_name, effect_size = effect_size)
}

# --- run sims & aggregate ---
results <- map(effect_sizes, function(Delta) {
  eps_lenient <- 0.5*Delta
  sims_UR <-  lapply(
    seeds, run_simulation_flex,
    method_func = UR_multi,
    Delta = Delta,
    eps_lenient = eps_lenient
  )
  sims_TS <- lapply(
    seeds, run_simulation_flex,
    method_func = TS_multi,
    Delta = Delta,
    eps_lenient = eps_lenient
  )
  sims_WAPTS <- lapply(
    seeds, run_simulation_flex,
    method_func = WAPTS_multi,
    Delta = Delta,
    rescue = FALSE,
    eps_lenient = eps_lenient
  )
  sims_WAPTS_rescue <- lapply(
    seeds, run_simulation_flex,
    method_func = WAPTS_multi,
    Delta = Delta,
    rescue = TRUE,
    eps_lenient = eps_lenient
  )
  sims_WAPTS_tempered <- lapply(
    seeds, run_simulation_flex,
    method_func = WAPTS_multi_tempered,
    Delta = Delta,
    rescue = FALSE,
    eta_schedule = "adaptive",
    eta_min = 0.2, eta_max = 1.0,
    eps_lenient = eps_lenient
  )
  sims_WAPTS_cs <- lapply(
    seeds, run_simulation_flex,
    method_func = WAPTS_multi_countscale_arm,
    Delta = Delta,
    rescue = FALSE,
    w_min = 0.2, w_max = 1.0, c = 20,
    eps_lenient = eps_lenient
  )
  bind_rows(
    aggregate_estimates(sims_UR,    "UR",    Delta),
    aggregate_estimates(sims_TS,    "TS",    Delta),
    aggregate_estimates(sims_WAPTS, "WAPTS", Delta),
    # aggregate_estimates(sims_WAPTS_rescue, "WAPTS_rescue", Delta)
    # aggregate_estimates(sims_WAPTS_tempered, "WAPTS_tempered", Delta),
    # aggregate_estimates(sims_WAPTS_cs, "WAPTS-CS",   Delta)
  )
})

combined_agg <- bind_rows(results) |>
  mutate(
    # method = factor(method, levels = c("TS", "WAPTS", "WAPTS_rescue")),
    method = factor(method, levels = c("UR", "TS", "WAPTS")),
    # method = factor(method, levels = c("TS", "WAPTS", "WAPTS_tempered", "WAPTS-CS")),
    effect_size_f = factor(effect_size, levels = effect_sizes,
                           labels = paste0("Effect Size = ", format(effect_sizes, nsmall = 2))),
    target = factor(target, levels = c(
      "Optimal arm (1): bias (posterior mean - true)",
      "Average reward up to t",
      "P(select optimal arm) up to t",
      "Avg epsilon-lenient regret up to t (eps=0.5*Delta)",
      "P(select truly bad arm) up to t (eps=0.5*Delta)"
    ))
  )

p <- ggplot(combined_agg,
            aes(x = horizon, y = estimate_mean,
                color = method, fill = method, linetype = method)) +
  geom_vline(xintercept = burnin, linetype = "longdash",
             color = "grey55", linewidth = 0.6, show.legend = FALSE) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.14, color = NA) +
  geom_line(linewidth = 1.1) +
  facet_grid(target ~ effect_size_f, scales = "free_y") +
  coord_cartesian(expand = FALSE) +
  scale_color_manual(values = c(UR = "yellow", TS = "#1f78b4", WAPTS = "#e31a1c", "WAPTS_rescue" = "purple", "WAPTS_tempered" = "orange","WAPTS-CS" = "green" ), name = "Policy") +
  scale_fill_manual( values = c(UR = "yellow", TS = "#1f78b4", WAPTS = "#e31a1c", "WAPTS_rescue" = "purple", "WAPTS_tempered" = "orange","WAPTS-CS" = "green"), name = "Policy") +
  scale_linetype_manual(values = c(UR = "longdash", TS = "longdash", WAPTS = "solid", "WAPTS_rescue" = 'solid', "WAPTS_tempered" = "solid","WAPTS-CS" = "solid"), name = "Policy") +
  labs(
    title = "Trajectories: (1) bias(posterior mean - true), (2) average reward, (3) P(select optimal), (4) Lenient Regret, (5) P(select bad)",
    x = "Time t",
    y = NULL
  ) +
  geom_hline(
        data = data.frame(target = "Optimal arm (1): bias (posterior mean - true)"),
        aes(yintercept = 0),
        color = "grey55", linewidth = 0.5, inherit.aes = FALSE
      ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position   = "bottom",
    strip.text        = element_text(size = 12, face = "bold"),
    panel.grid.minor  = element_blank()
  )

print(p)


# To Save the Output
p <- p + theme(
  plot.margin = ggplot2::margin(10, 80, 10, 10),
  strip.text.y.right = element_text(angle = 0)
)

ggsave("only_opt_plot.png_flexible_gap.png", plot = p, width = 14, height = 7, dpi = 300)
```

### Part II-1.2 Fixed Gap Setting:

```{r}
library(dplyr)
library(ggplot2)
library(purrr)

# --- settings ---
burnin    <- 10
n         <- 239
seeds     <- 1024:3024
effect_sizes <- c(0.05, 0.10, 0.20, 0.30)
theta_min <- 0.50

# Generate success rates for flexible gap with a unique best arm
gen_rates_flex <- function(K = 10, theta_min = 0.5, Delta = 0.1, eps = 1e-6) {
  theta_star <- theta_min + Delta
  subs <- rep(0.5, K-1)
  c(theta_star, subs)  # optimal arm at index 1
}

run_simulation_flex <- function(seed, method_func, Delta, ..., eps_lenient) {
  set.seed(seed)
  rates <- gen_rates_flex(K = 10, theta_min = theta_min, Delta = Delta)

  out <- method_func(success_rates = rates, burnin = burnin, n = n, ...)

  Succ <- out$arm_success_history
  Fail <- out$arm_failure_history

  # ---- Track A: optimal arm posterior mean (empirical) ----
  s_opt <- Succ[1, ]
  f_opt <- Fail[1, ]
  tot_opt <- s_opt + f_opt
  est_opt <- ifelse(tot_opt > 0, s_opt / tot_opt, NA_real_)

  # ---- Track B: empirical average reward up to time t ----
  y <- as.numeric(out$history)           # 0/1 reward each step
  avg_reward <- cumsum(y) / seq_len(n)   # cummean

  # ---- Track C: probability of selecting the correct arm up to time t ----
  chosen <- as.integer(out$arm_selected)
  p_correct <- cumsum(chosen == 1L) / seq_len(n)

  # ---- Track D: epsilon-lenient regret up to time t ----
  # r_t^eps = max(0, (theta* - eps) - theta_{a_t})
  theta_star <- max(rates)
  theta_chosen <- rates[chosen]
  inst_regret_eps <- pmax(0, (theta_star - eps_lenient) - theta_chosen)
  regret_eps_cummean <- cumsum(inst_regret_eps) / seq_len(n)

  # ---- Track E: probability of selecting a truly bad arm up to time t ----
  # truly bad: theta_k < theta* - eps
  bad_set <- which(rates < (theta_star - eps_lenient))
  is_bad <- chosen %in% bad_set
  p_bad <- cumsum(is_bad) / seq_len(n)

  data.frame(
    horizon  = rep(seq_len(n), times = 5),
    estimate = c(est_opt, avg_reward, p_correct, regret_eps_cummean, p_bad),
    target   = rep(c(
      "Optimal arm (1): posterior mean",
      "Average reward up to t",
      "P(select optimal arm) up to t",
      "Avg epsilon-lenient regret up to t (eps=0.5*Delta)",
      "P(select truly bad arm) up to t (eps=0.5*Delta)"
    ), each = n)
  )
}


aggregate_estimates <- function(sim_list, method_name, effect_size) {
  bind_rows(sim_list, .id = "rep") |>
    group_by(target, horizon) |>
    summarise(
      estimate_mean = mean(estimate, na.rm = TRUE),
      ci_lower      = quantile(estimate, 0.025, na.rm = TRUE),
      ci_upper      = quantile(estimate, 0.975, na.rm = TRUE),
      .groups = "drop"
    ) |>
    mutate(method = method_name, effect_size = effect_size)
}

# --- run sims & aggregate ---
results <- map(effect_sizes, function(Delta) {
  eps_lenient <- 0.5*Delta
  sims_TS <- lapply(
    seeds, run_simulation_flex,
    method_func = TS_multi,
    Delta = Delta,
    eps_lenient = eps_lenient
  )
  sims_WAPTS <- lapply(
    seeds, run_simulation_flex,
    method_func = WAPTS_multi,
    Delta = Delta,
    rescue = FALSE,
    eps_lenient = eps_lenient
  )
  sims_WAPTS_rescue <- lapply(
    seeds, run_simulation_flex,
    method_func = WAPTS_multi,
    Delta = Delta,
    rescue = TRUE,
    eps_lenient = eps_lenient
  )
  sims_WAPTS_tempered <- lapply(
    seeds, run_simulation_flex,
    method_func = WAPTS_multi_tempered,
    Delta = Delta,
    rescue = FALSE,
    eta_schedule = "adaptive",
    eta_min = 0.2, eta_max = 1.0,
    eps_lenient = eps_lenient
  )
  sims_WAPTS_cs <- lapply(
    seeds, run_simulation_flex,
    method_func = WAPTS_multi_countscale_arm,
    Delta = Delta,
    rescue = FALSE,
    w_min = 0.2, w_max = 1.0, c = 20,
    eps_lenient = eps_lenient
  )
  bind_rows(
    aggregate_estimates(sims_TS,    "TS",    Delta),
    aggregate_estimates(sims_WAPTS, "WAPTS", Delta),
    # aggregate_estimates(sims_WAPTS_rescue, "WAPTS_rescue", Delta)
    # aggregate_estimates(sims_WAPTS_tempered, "WAPTS_tempered", Delta),
    # aggregate_estimates(sims_WAPTS_cs, "WAPTS-CS",   Delta)
  )
})

combined_agg <- bind_rows(results) |>
  mutate(
    # method = factor(method, levels = c("TS", "WAPTS", "WAPTS_rescue")),
    method = factor(method, levels = c("TS", "WAPTS")),
    # method = factor(method, levels = c("TS", "WAPTS", "WAPTS_tempered", "WAPTS-CS")),
    effect_size_f = factor(effect_size, levels = effect_sizes,
                           labels = paste0("Effect Size = ", format(effect_sizes, nsmall = 2))),
    target = factor(target, levels = c(
      "Optimal arm (1): posterior mean",
      "Average reward up to t",
      "P(select optimal arm) up to t",
      "Avg epsilon-lenient regret up to t (eps=0.5*Delta)",
      "P(select truly bad arm) up to t (eps=0.5*Delta)"
    ))
  )

p <- ggplot(combined_agg,
            aes(x = horizon, y = estimate_mean,
                color = method, fill = method, linetype = method)) +
  geom_vline(xintercept = burnin, linetype = "longdash",
             color = "grey55", linewidth = 0.6, show.legend = FALSE) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.14, color = NA) +
  geom_line(linewidth = 1.1) +
  coord_cartesian(expand = FALSE) +
  facet_grid(target ~ effect_size_f) +
  scale_color_manual(values = c(TS = "#1f78b4", WAPTS = "#e31a1c", "WAPTS_rescue" = "purple", "WAPTS_tempered" = "orange","WAPTS-CS" = "green" ), name = "Policy") +
  scale_fill_manual( values = c(TS = "#1f78b4", WAPTS = "#e31a1c", "WAPTS_rescue" = "purple", "WAPTS_tempered" = "orange","WAPTS-CS" = "green"), name = "Policy") +
  scale_linetype_manual(values = c(TS = "longdash", WAPTS = "solid", "WAPTS_rescue" = 'solid', "WAPTS_tempered" = "solid","WAPTS-CS" = "solid"), name = "Policy") +
  labs(
    title = "Trajectories: (1) optimal arm mean, (2) average reward, (3) P(select optimal), (4) Lenient Regret, (5) P(select bad)",
    x = "Time t",
    y = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position   = "bottom",
    strip.text        = element_text(size = 12, face = "bold"),
    panel.grid.minor  = element_blank()
  )

print(p)


# To Save the Output
p <- p + theme(
  plot.margin = ggplot2::margin(10, 80, 10, 10),
  strip.text.y.right = element_text(angle = 0)
)

ggsave("only_opt_plot.png_fixed_gap.png", plot = p, width = 14, height = 7, dpi = 300)
```

## Part II-2 Experiment Setup of multiple Optimal Arm.

In this setup, in the simulation setting, we have `M` arms out of the
`K` arms to be truly optimal, where `M <= K` .

The rest of the arm is uniformly distributed from the range
`(0.5, 0.5 + effect size - 10e-6).` We will plan out the simulation
setting and plot the posterior mean estimate of the optimal arm, the
average reward comparison, and the probability of selecting the optimal
arm.

```{r}
library(dplyr)
library(ggplot2)
library(purrr)

# --- settings ---
burnin      <- 10
n           <- 239
seeds       <- 1024:3024
effect_sizes <- c(0.05, 0.10, 0.20, 0.30)
theta_min   <- 0.50
K           <- 10
M_opt       <- 4   # optimal arms are indices 1:M_opt

# ----------------------------
# Generate success rates with M optimal arms and K-M suboptimal arms
# ----------------------------
gen_rates_multiopt <- function(K = 10, M = 4, theta_min = 0.5, Delta = 0.1, eps = 1e-6) {
  stopifnot(M >= 1, M < K)
  theta_star <- theta_min + Delta

  optimal <- rep(theta_star, M)
  subs <- pmin(runif(K - M, min = theta_min, max = theta_star), theta_star - eps)

  c(optimal, subs)
}

# ----------------------------
# One simulation run: return trajectories for
# (A) mean estimate over optimal arms (1:M)
# (B) empirical average reward up to time t
# (C) P(select optimal arm) up to time t
# ----------------------------
run_simulation_multiopt <- function(seed, method_func, Delta, K = 10, M = 4, ...) {
  set.seed(seed)

  rates <- gen_rates_multiopt(K = K, M = M, theta_min = theta_min, Delta = Delta)
  out <- method_func(success_rates = rates, burnin = burnin, n = n, ...)

  Succ <- out$arm_success_history  # K x n
  Fail <- out$arm_failure_history  # K x n

  # ---- Track A: pooled empirical mean across ALL optimal arms (1:M) ----
  est_opt_group <- vapply(seq_len(n), function(t) {
    s <- sum(Succ[1:M, t])
    f <- sum(Fail[1:M, t])
    tt <- s + f
    if (tt > 0) s / tt else NA_real_
  }, numeric(1))

  # ---- Track B: empirical average reward up to time t ----
  y <- as.numeric(out$history)          # 0/1 reward each step
  avg_reward <- cumsum(y) / seq_len(n)  # cummean reward

  # ---- Track C: running probability of selecting an optimal arm (1:M) ----
  chosen <- as.integer(out$arm_selected)
  is_opt <- chosen %in% seq_len(M)
  p_select_opt <- cumsum(is_opt) / seq_len(n)

  data.frame(
    horizon  = rep(seq_len(n), times = 3),
    estimate = c(est_opt_group, avg_reward, p_select_opt),
    target   = rep(c(
      paste0("Optimal arms (1–", M, ") mean"),
      "Average reward up to t",
      paste0("P(select optimal arm in 1–", M, ") up to t")
    ), each = n)
  )
}

# ----------------------------
# Aggregate across simulation reps into mean and 95% interval band
# ----------------------------
aggregate_estimates <- function(sim_list, method_name, effect_size) {
  bind_rows(sim_list, .id = "rep") |>
    group_by(target, horizon) |>
    summarise(
      estimate_mean = mean(estimate, na.rm = TRUE),
      ci_lower      = quantile(estimate, 0.025, na.rm = TRUE),
      ci_upper      = quantile(estimate, 0.975, na.rm = TRUE),
      .groups = "drop"
    ) |>
    mutate(method = method_name, effect_size = effect_size)
}

# ----------------------------
# Run sims & aggregate for each effect size
# ----------------------------
results <- map(effect_sizes, function(Delta) {
  sims_TS <- lapply(
    seeds, run_simulation_multiopt,
    method_func = TS_multi, Delta = Delta, K = K, M = M_opt
  )

  sims_WAPTS <- lapply(
    seeds, run_simulation_multiopt,
    method_func = WAPTS_multi, Delta = Delta, K = K, M = M_opt,
    rescue = FALSE
  )

  bind_rows(
    aggregate_estimates(sims_TS,    "TS",    Delta),
    aggregate_estimates(sims_WAPTS, "WAPTS", Delta)
  )
})

combined_agg <- bind_rows(results) |>
  mutate(
    method = factor(method, levels = c("TS", "WAPTS")),
    effect_size_f = factor(
      effect_size,
      levels = effect_sizes,
      labels = paste0("Effect Size = ", format(effect_sizes, nsmall = 2))
    ),
    target = factor(
      target,
      levels = c(
        paste0("Optimal arms (1–", M_opt, ") mean"),
        "Average reward up to t",
        paste0("P(select optimal arm in 1–", M_opt, ") up to t")
      )
    )
  )

# ----------------------------
# Plot
# ----------------------------
p <- ggplot(
  combined_agg,
  aes(x = horizon, y = estimate_mean,
      color = method, fill = method, linetype = method)
) +
  geom_vline(
    xintercept = burnin, linetype = "longdash",
    color = "grey55", linewidth = 0.6, show.legend = FALSE
  ) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.14, color = NA) +
  geom_line(linewidth = 1.1) +
  coord_cartesian(ylim = c(0, 1), expand = FALSE) +
  facet_grid(target ~ effect_size_f) +
  scale_color_manual(values = c(TS = "#1f78b4", WAPTS = "#e31a1c"), name = "Policy") +
  scale_fill_manual( values = c(TS = "#1f78b4", WAPTS = "#e31a1c"), name = "Policy") +
  scale_linetype_manual(values = c(TS = "solid", WAPTS = "longdash"), name = "Policy") +
  labs(
    title    = "Trajectories with multiple optimal arms",
    subtitle = paste0("K=", K, ", optimal arms=", M_opt),
    x = "Time t",
    y = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position   = "bottom",
    strip.text        = element_text(size = 12, face = "bold"),
    panel.grid.minor  = element_blank()
  )

print(p)

# To Save the Output Graph

p <- p + theme(
  plot.margin = ggplot2::margin(10, 80, 10, 10),
  strip.text.y.right = element_text(angle = 0)
)

ggsave("multi_opt_plot.png", plot = p, width = 14, height = 7, dpi = 300)
```
